---
title: "Homework 6"
author: "Phoebe Mo"
date: "2020-12-4"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(rvest)
library(dplyr)
library(HH)
library(corrplot)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis",
  digits = 3
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Read in the data
```{r}
homicide_df =
  read_csv("Data/homicide-data.csv", na = c("", "NA", "Unknown")) %>%
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest" ~ 0,
      disposition == "Closed by arrest" ~ 1
    )
  ) %>%
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>%
    dplyr::select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with only one city.
```{r}
baltimore_df =
  homicide_df %>%
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex,
    data = baltimore_df,
    family = binomial()) %>%
  broom::tidy() %>%
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>%
  dplyr::select(term, OR, starts_with("CI")) %>%
  knitr::kable(digits = 3)
```

Try this across cities.
```{r}
models_results_df =
  homicide_df %>%
  nest(data = -city_state) %>%
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
      results = map(models, broom::tidy)
  ) %>%
  dplyr::select(city_state, results) %>%
  unnest(results) %>%
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>%
  dplyr::select(city_state, term, OR, starts_with("CI"))
```

```{r}
models_results_df %>%
  filter(term == "victim_raceWhite") %>%
  mutate(city_state = fct_reorder(city_state, OR)) %>%
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
In the plot, the OR is mostly greater than 1, meaning it is less likely that homicide happens in the Black race than the White race.

## Problem 2

read in data and manipulation
```{r}
bw_df =
  read_csv("Data/birthweight.csv")
```

stepwise regression to find find suitable predictors
```{r}
# checking collinearity
par(mar = c(4,5,1,1))
cor(bw_df %>% dplyr::select(-c(pnumlbw, pnumsga))) %>%
  corrplot(method = "circle", type = "upper", diag = FALSE)

# delwt and ppwt have high correlation; mrace and frace have high correlation; ppbmi and ppwt have high correlation; so we preserve one of them in each high correlation pair; pnumlbw and pnumsga are dropped becasue all entries for them are 0

# backward regression
stepOne = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + malform + menarche + mheight + momage + mrace + parity + ppbmi + smoken + wtgain, data = bw_df) %>% broom::tidy()

# exclude ppbmi which p-value = 0.945
stepTwo = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + malform + menarche + mheight + momage + mrace + parity + smoken + wtgain, data = bw_df) %>% broom::tidy()

# exclude malform which p-value = 0.837
stepThree = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + menarche + mheight + momage + mrace + parity + smoken + wtgain, data = bw_df) %>% broom::tidy()

# exclude menarche which p-value = 0.14
stepFinal = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + momage + mrace + parity + smoken + wtgain, data = bw_df)
```

After solving for collinearity and using backward regression to select reasonable predictors for my model, I include 12 variables as predictors. 

delwt and ppwt have high correlation; mrace and frace have high correlation; ppbmi and ppwt have high correlation; so we preserve one of them in each high correlation pair; pnumlbw and pnumsga are dropped becasue all entries for them are 0.

In the backward regression, ppbmi, malform, and menarche are dropped in order.

Here is a plot showing residuals against fitted values for my model
```{r}
# make a plot of model residuals against fitted values
bw_df %>%
  add_predictions(stepFinal) %>%
  add_residuals(stepFinal) %>%
  ggplot(aes(x = pred, y = resid)) +
  geom_point(color = 'lightpink')
```

We can see from the plot: the residuals are bouncing around 0 and indicates a quite equal variance.

Next, compare my model to the two given models through CV

```{r}
model_two = lm(bwt ~ blength + gaweeks, data = bw_df)
model_three = lm(bwt ~ bhead * blength * babysex, data = bw_df)

cv_df = crossv_mc(bw_df, 100) %>%
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  ) %>%
  mutate(
    my_mod = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + momage + mrace + parity + smoken + wtgain, data = .x)),
    second_mod = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    third_mod = map(train, ~lm(bwt ~ bhead * blength * babysex, data = .x))
  ) %>%
  mutate(
    rmse_my = map2_dbl(my_mod, test, ~rmse(model = .x, data = .y)),
    rmse_second = map2_dbl(second_mod, test, ~rmse(model = .x, data = .y)),
    rmse_third = map2_dbl(third_mod, test, ~rmse(model = .x, data = .y))
  )

cv_df %>%
  dplyr::select(starts_with("rmse")) %>%
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>%
  mutate(model = fct_inorder(model)) %>%
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

As can see from the plot showing the cross-validated prediction errors(rmse) for each model, my diy model performs the best and has the lease median of rmse.


## Problem 3

